A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-10-20 evaluation.tex
Something
New ostrich

The benchmarks are executed in parallel across a cluster of \Fudge{identical}
machines, \BenchmarkRig{}, but as the sole job for each machine.  We compiled
the code using Scala~\ScalaVersion{} and executed the experiments
on~\JvmVersion{} with a maximum heap of~\MaxHeapSize{}. We used \Nuxmv{}
version~\NuxmvVersion{} invoked as a subprocess for each instance. Instances
were executed in batches of \BatchSize{}, each given a fresh JVM. Each JVM was
warmed up for \numprint{10}s on a random benchmark from the set before starting
to execute. We believe this represents a realistic use case where \Calculus{} is
used to support, e.g., a string solver. Experiments were executed in random order
for all backends. Each instance got a time budget of~\RuntimeTimeout.

@@

In \cref{fig:solve-division}, we show how many of the~\NrBenchmarks{} instances
the respective back-end could solve. A summary of their outcomes by instance
type is also available in \cref{tab:solve-status}. Note that many instances lack
a corum ground truth as they are solved by only one backend. We see that
\Calculus{} generally outperforms \Nuxmv{} on determining unsatisfiability, as
does baseline, while being similar at satisfiable instances. Both \Calculus{} and
\Nuxmv outperforms baseline on satisfiable instances. On satisfiable
instances, \Nuxmv and \Calculus{} have similar performance.

@@

\begin{table}
  \begin{center}
  \input{graphs/solved_smt_comp.tex}
  \end{center}
  \caption{Number of solved benchmarks, on a subset of 1000
    PyEx benchmarks from SMT-COMP.}\label{tab:solve-status-smt-comp}
\end{table}

>>>>

The benchmarks are executed in parallel across a cluster of identical
machines, \BenchmarkRig{}, but as the sole job for each machine.  We compiled
the code using Scala~\ScalaVersion{} and executed the experiments
on~\JvmVersion{} with a maximum heap of~\MaxHeapSize{}. We used \Nuxmv{}
version~\NuxmvVersion{} invoked as a subprocess for each instance. Instances
were executed in batches of \BatchSize{}, each given a fresh JVM. Each JVM was
warmed up for \numprint{10}s on a random benchmark from the set before starting
to execute. We believe this represents a realistic use case where \Calculus{} is
used to support, e.g., a string solver. Experiments were executed in random order
for all backends. Each instance got a time budget of~\RuntimeTimeout.

@@

In \cref{fig:solve-division}, we show how many of the~\NrBenchmarks{} instances
the respective back-end could solve. A summary of their outcomes by instance
type is also available in \cref{tab:solve-status}. Note that many instances lack
a corum ground truth as they are solved by only one backend. We see that
\Calculus{} generally outperforms \Nuxmv{} on determining unsatisfiability, as
does baseline, while being similar at satisfiable instances. Both \Calculus{} and
\Nuxmv{} outperforms baseline on satisfiable instances. On satisfiable
instances, \Nuxmv and \Calculus{} have similar performance.

@@

\begin{table}
  \begin{center}
  \input{experiments/qf_slia_comparison.tex}
  \end{center}
  \caption{Number of solved benchmarks from the single-query QF\_SLIA track of
  quantifier-free string linear integer arithmetic at SMT-COMP 2023. The numbers
  for each solver are from the publicly available data files, except for
  \Ostrich-\Catra{}, which are executed by us. }\label{tab:solve-status-smt-comp}
\end{table}
